---
title: "Project Q1"
output: html_notebook
---

 
Question: correlation between price and sales.

Reading data:
```{r}
sales_data_df <- read.csv(file = '~/Desktop/MDSA/602/Project/summer-products-with-rating-and-performance_2020-08.csv')
```

```{r}
head(sales_data_df)
```

```{r}
unique(sales_data_df[c("units_sold")])
```
```{r}
sales_data_df %>% group_by(units_sold) %>%tally()
```

H0: mean sale prices for products sold over 5000 units is same as product sold less than 1000 units.

mean_retail_price_100 = mean_retail_price_5000

HA: mean sale prices for products sold over 5000 is less than price of products less 1000 units.

mean_retail_price_100 = mean_retail_price_5000

Carrying out proportion test

1. Data Preparation

Filtering out required columns.
```{r}
q1_df = data.frame(price = sales_data_df$price, retail_price = sales_data_df$retail_price, units_sold = sales_data_df$units_sold)
```

```{r}
head(q1_df)
```


Combining "units_sold" with values less than 100 into the category of 100 product_sold.

```{r}
q1_df$units_sold <- factor(q1_df$units_sold)
```

```{r}
levels(q1_df$units_sold)
```


```{r}
levels(q1_df$units_sold) <- list("100"=c("1", "2", "3", "6", "7", "8", "10", "50", "100"),"5000"=c("5000", "10000", "20000", "50000", "100000"))
```

```{r}
q1_df %>% group_by(units_sold) %>%tally()
```

Removing NA values.

```{r}
q1_df <- na.omit(q1_df)
```

2. Visual analysis.
```{r}
ggplot(data=q1_df, aes(x = units_sold, y = retail_price)) + geom_violin(fill="blue") + geom_boxplot(width = 0.1, fill="orange") + xlab("Units Sold") + ylab("Retail price of products") + ggtitle("Violin plot of retail prices") + coord_flip()
```

3. Creating distribution of bootstrap statistics for the difference in means.
```{r}
ntrials = 1000
n.sold_100 = favstats(~retail_price|units_sold, data=q1_df)$n[1]
n.sold_5000 = favstats(~retail_price|units_sold, data=q1_df)$n[2]
n.sold_100
n.sold_5000
```

```{r}
mean.sold_100 = numeric(ntrials)
mean.sold_5000 = numeric(ntrials) 
diffmeanssold = numeric(ntrials)
units_sold_100 = filter(q1_df, units_sold=="100")
units_sold_5000 = filter(q1_df, units_sold=="5000")
```

```{r}
head(units_sold_100)
```
```{r}
head(units_sold_5000)
```

```{r}
for(i in 1:ntrials)
{   mean.sold_100[i] = mean(sample(units_sold_100$retail_price, n.sold_100, replace=TRUE))
    mean.sold_5000[i] = mean(sample(units_sold_5000$retail_price, n.sold_5000, replace=TRUE))
    diffmeanssold[i] = mean.sold_100[i] - mean.sold_5000[i]
}
boot_diffmeanssold = data.frame(mean.sold_100, mean.sold_5000, diffmeanssold)
```

```{r}
head(boot_diffmeanssold)
```

```{r}
ggplot(data=boot_diffmeanssold, aes(x = diffmeanssold)) + geom_histogram(fill='blue', col='red', binwidth=1) + xlab("Difference Between Mean of units sold") + ggtitle("Distribution of Mean(100 units) - Mean(5000 units)")
```

4. Building 95% confidence interval.
```{r}
qdata(~ diffmeanssold, c(0.025, 0.975), data=boot_diffmeanssold)
```

It can be observed that 0 lies between the confidence interval of -2.1186 - 4.5659.

Since we have significantly more number of sample count, validating our confidence interval using a t-test.
```{r}
t.test(~retail_price|units_sold, conf.level=0.95, alternative = "two.sided", var.equal=FALSE, q1_df)
```
Since p-value of 0.4958 > alpha(0.05), we cannot reject our null hypothesis.
Hence, there is no difference in means of products that are sold less than 100 units versus products sold over 5000. This can mean that though price is a factor for customers to buy a product, it is not the main factor affecting the sales of the respective products.

